Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-13 paper/paper-conf.tex
Recreated graphs with pgfplots (and more)

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

@@

\begin{table*}
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Comparison of intensity transformations under Dasgupta--Pal}
	\label{tbl:it-dp}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-pal} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem. Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.

@@

\begin{table}[h]
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
    \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Image negation under Dasgupta--Pal}
	\label{tbl:neg-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Logarithm transformation under Dasgupta--Pal}
	\label{tbl:log-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\caption{Power-law transformation under Dasgupta--Pal}
	\label{tbl:pwr-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.277 & 9261.407 & 0.150 \\
		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.257 & 9259.010 & 0.051 \\
		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.279 & 9440.351 & 0.051 \\
		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.285 & 9492.149 & 0.052 \\
		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.289 & 9321.928 & 0.048 \\
		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.257 & 9233.818 & 0.048 \\
		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.262 & 9203.045 & 0.048 \\
		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.258 & 9210.393 & 0.048 \\
		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
		\bottomrule
        \end{tabular}
\end{table}

>>>>

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix~\ref{sec:approx-pwr}.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

@@

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under Dasgupta--Pal}
	\label{tbl:it-dp}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule
	\end{tabular}
\end{table*}

Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem. Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.

@@

\begin{table}[h]
	\centering
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
    \end{tabular}
\end{table}
\begin{table}[h]
	\centering
	\caption{Image negation under Dasgupta--Pal}
	\label{tbl:neg-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Logarithm transformation under Dasgupta--Pal}
	\label{tbl:log-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Power-law transformation under Dasgupta--Pal}
	\label{tbl:pwr-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
		\texttt{bplyce} & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
		\texttt{drbost} & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
		\texttt{ksunth} & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
		\texttt{martin} & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
		\texttt{pmives} & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
		\texttt{rnpwil} & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
		\texttt{sbains} & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
		\texttt{swewin} & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
		\texttt{yfhsie} & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
		\bottomrule
        \end{tabular}
\end{table}
